---
title: "experiment 2"
format: html
editor: visual
---

## Import packages

```{r,  echo=FALSE,}
library(conflicted)  
conflict_prefer("filter", "dplyr")
conflict_prefer("lag", "dplyr")
library(plotly)
library(tidyverse)
library(tidyboot)
library(lme4)
library(here)
library(jsonlite)
library(ggthemes)

theme_set(theme_few())
```

## Read in data

```{r,  echo=FALSE, message=FALSE, warning=FALSE}

d.all <- read_csv(here('analysis/2_experiment_2/exp2_clean_data_jan17.csv'))

d.all <- d.all %>%
  separate(treatmentName.x, into = c("direction", "treatment"), sep = "_")

d.all <- d.all %>%
  mutate(error = if_else(direction == "RS", abs((100-guess) - (mleGame*100)), abs(guess - (mleGame*100))))
```

## Filter games with 2+ inactive players

```{r}
persistentnoClick <- data.frame(gameID = character(), playerID = character(), stringsAsFactors = FALSE)

for (i in 1:7) {
  idx_pair <- c(i + 1, i + 2)
    filtered_players <- d.all %>%
    group_by(gameID, playerID) %>%
    filter(all(is.na(guess[idx_pair]))) %>%
    select(gameID, playerID) %>%
    distinct()
    persistentnoClick <- bind_rows(persistentnoClick, filtered_players)
}
persistentnoClick <- distinct(persistentnoClick)

gameIDs_to_remove <- persistentnoClick %>%
  count(gameID) %>%
  filter(n >= 2) %>%
  pull(gameID)

d.all <- d.all %>%
  filter(!(gameID %in% gameIDs_to_remove)) 

d.allnovel <-d.all %>%
  filter(is.na(designatedGame))%>%
  distinct(gameID)

d.allgame <- d.all %>%
   distinct(gameID, .keep_all = TRUE)

d.all <- d.all %>%
  mutate(
    nCrittersGame_bin = str_remove_all(nCrittersGame_bin, "[\\[\\]()]"),
    entropy_bin = str_remove_all(entropy_bin, "[\\[\\]()]"),
    representation_bin = str_remove_all(representation_bin, "[\\[\\]()]")
  )
```

# count of games in each information condition

```{r}
heatmap_test <- d.allgame %>%
  group_by(treatment, direction, nCrittersGame_bin, representation_bin) %>%
  summarise(count = n(), .groups = "drop") %>%
  mutate(prop = count / sum(count, na.rm = TRUE))

ggplot(heatmap_test, aes(x = representation_bin, y = nCrittersGame_bin)) +
  geom_tile(aes(fill = count), color = "white") +
  scale_fill_gradient(name = "Count of Games", low = "lightblue", high = "darkblue") +
  labs(x = "Representation", y = "nCrittersGame") +
  theme_few() +
  theme(
    aspect.ratio = 1,
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  facet_wrap(~treatment #+ direction
             )
heatmap_test <- d.allgame %>%
  group_by(treatment, direction, entropy_bin, representation_bin) %>%
  summarise(count = n()) %>%
  mutate(prop = count / sum(count))

ggplot(heatmap_test, aes(x = entropy_bin, y = representation_bin)) +
  geom_tile(aes(fill = count), color = "white") +
  scale_fill_gradient(name = "Count of Games", low = "lightblue", high = "darkblue") +
  labs(x = "entropy", y = "representation") +
  theme_few() +
  theme(
    aspect.ratio = 1, axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  facet_wrap(~treatment #+ direction
            )

nCritters_entropy_heatmap_new <- d.allgame %>%
  group_by(treatment, direction, nCrittersGame_bin, entropy_bin) %>%
  summarise(count = n()) %>%
  mutate(prop = count / sum(count))

ggplot(nCritters_entropy_heatmap_new, aes(x = entropy_bin, y = nCrittersGame_bin)) +
  geom_tile(aes(fill = count), color = "white") +
  scale_fill_gradient(name = "Count of Games", low = "lightblue", high = "darkblue") +
  labs(x = "Entropy", y = "nCrittersGame") +
  theme_few() +
  theme(
    aspect.ratio = 1, axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  facet_wrap(~treatment #+ direction
            )

```

# count of no data entered over rounds

```{r}
d.all %>%
  group_by(idx) %>%
  summarise(na_count = sum(is.na(error))) %>%
  ggplot(aes(x = idx, y = na_count)) +
  geom_line() +
  labs(x = "Index", y = "NA Count", title = "NA Count Over Time") +
  theme_minimal()

```

# error between slider and interactive condition

```{r}

heatmap_test <- d.all%>%
  filter(idx ==8) %>%
  group_by(representation_bin, nCrittersGame_bin, treatment) %>%
  summarize(errorAvg = mean(error, na.rm = TRUE)) 


ggplot(heatmap_test, aes(x = representation_bin, y = nCrittersGame_bin)) +
  geom_tile(aes(fill = errorAvg), color = "white") +  # Fill by error
  scale_fill_gradient(name = "Error", low = "lightblue", high = "darkblue") +  # Adjust scale
  labs(x = "Representation", y = "nCrittersGame") +
  theme_few() +
  theme(
    aspect.ratio = 1,
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  facet_wrap(~treatment) 

heatmap_test_2 <- d.all%>%
  filter(idx ==8) %>%
  group_by(entropy_bin, nCrittersGame_bin, treatment) %>%
  summarize(errorAvg = mean(error, na.rm = TRUE))

ggplot(heatmap_test_2, aes(x = entropy_bin, y = nCrittersGame_bin)) +
  geom_tile(aes(fill = errorAvg), color = "white") +  # Fill by error
  scale_fill_gradient(name = "Error", low = "lightblue", high = "darkblue") +  # Adjust scale
  labs(x = "Entropy", y = "nCrittersGame") +
  theme_few() +
  theme(
    aspect.ratio = 1,
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  facet_wrap(~treatment) 

heatmap_test_3 <- d.all%>%
  filter(idx ==8) %>%
  group_by(representation_bin, entropy_bin, treatment) %>%
  summarize(errorAvg = mean(error, na.rm = TRUE))

ggplot(heatmap_test_3, aes(x = entropy_bin, y = representation_bin)) +
  geom_tile(aes(fill = errorAvg), color = "white") +  # Fill by error
  scale_fill_gradient(name = "Error", low = "lightblue", high = "darkblue") +  # Adjust scale
  labs(x = "Entropy", y = "Representation") +
  theme_few() +
  theme(
    aspect.ratio = 1,
    
    axis.text.x = element_text(angle = 45, hjust = 1)
  ) +
  facet_wrap(~treatment)
```

# error differences in slider direction

```{r}
d.all %>%  
  group_by(treatment, direction, idx, gameID, mleGame) %>%
  summarize(error = if_else(direction == "RS", abs((100-guess) - (mleGame*100)), abs(guess - (mleGame*100)))) %>%
  group_by(treatment, idx, direction) %>%
  tidyboot::tidyboot_mean(error, na.rm = T) %>%
  ggplot(aes(x = idx, y = empirical_stat, color = treatment, linetype = treatment == 'interactive')) +
    geom_point() +
    geom_smooth(method = 'lm', formula = y ~ poly(x, 2), se = F) +
    geom_hline(yintercept = c(0), linetype = 'dotted') +
    theme_few() +
    scale_color_brewer(palette = 'Accent') +
    guides(linetype = 'none') +
    scale_x_continuous(breaks = c(1,3,5,7,9,11)) +
    labs(y = 'average error', x = 'round #', color = '')  +
    theme(aspect.ratio = 1, legend.position = 'top') +
  facet_wrap(~direction)

```

# error differences in calculator useage

```{r}
d.all_calc <- d.all %>%
  mutate(usedCalculator = case_when(
    exitSurvey == '{"usedCalculator":"no"}' ~ 'no',
    exitSurvey == '{"usedCalculator":"yes"}' ~ 'yes',
    TRUE ~ NA_character_
  )) %>%
  filter(usedCalculator %in% c('yes', 'no')) 

d.all_calc %>%  
  group_by(treatment, direction, idx, gameID, mleGame, usedCalculator) %>%
  reframe(error = if_else(direction == "RS", abs((100-guess) - (mleGame*100)), abs(guess - (mleGame*100)))) %>%
  filter(!is.na(error)) %>%  # Remove any rows where error is NA
  group_by(treatment, idx, direction, usedCalculator) %>%
  tidyboot::tidyboot_mean(error) %>%  
  ggplot(aes(x = idx, y = empirical_stat, color = treatment, linetype = treatment == 'interactive')) +
    geom_point() +
    geom_smooth(method = 'lm', formula = y ~ poly(x, 2), se = FALSE) +
    geom_hline(yintercept = c(0), linetype = 'dotted') +
    theme_few() +
    scale_color_brewer(palette = 'Accent') +
    guides(linetype = 'none') +
    scale_x_continuous(breaks = c(1,3,5,7,9,11)) +
    labs(y = 'average error', x = 'round #', color = '') +
    theme(aspect.ratio = 1, legend.position = 'top') +
  facet_wrap(~usedCalculator)

```

# error heatmap

```{r}

heatmap_test_3d_slider <- d.all %>%
  
  group_by(representation_bin, entropy_bin, nCrittersGame_bin, treatment) %>%
  summarize(errorAvg = mean(error, na.rm = TRUE), .groups = "drop")%>%
  filter(treatment == 'slider')

heatmap_test_3d_interactive <- d.all %>%
  
  group_by(representation_bin, entropy_bin, nCrittersGame_bin, treatment) %>%
  summarize(errorAvg = mean(error, na.rm = TRUE), .groups = "drop")%>%
  filter(treatment == 'interactive')

plot_ly(
  data = heatmap_test_3d_slider,
  x = ~representation_bin,
  y = ~entropy_bin,
  z = ~nCrittersGame_bin,
  color = ~errorAvg,  # color by errorAvg
  colors = c("lightgreen", "darkblue"),
  type = "scatter3d",
  mode = "markers",
  marker = list(size = 10, opacity = 0.8)
) %>%
  plotly::layout(
    title = "3D Cube Heatmap",
    scene = list(
      xaxis = list(title = "Representation"),
      yaxis = list(stitle = "Entropy"),
      zaxis = list(title = "nCrittersGame")
    )
  )

plot_ly(
  data = heatmap_test_3d_interactive,
  x = ~representation_bin,
  y = ~entropy_bin,
  z = ~nCrittersGame_bin,
  color = ~errorAvg,  # color by errorAvg
  colors = c("lightgreen", "darkblue"),
  type = "scatter3d",
  mode = "markers",
  marker = list(size = 10, opacity = 0.8)
) %>%
  plotly::layout(
    title = "3D Cube Heatmap",
    scene = list(
      xaxis = list(title = "Representation"),
      yaxis = list(stitle = "Entropy"),
      zaxis = list(title = "nCrittersGame")
    )
  )
```

# error across different information difficulties in different conditions

```{r}

d.all_minmax <- d.all %>%  mutate(
    entropy_median = median(entropy),
    representation_median = median(representation),
    nCrittersGame_median = median(nCrittersGame)
  ) %>%
  mutate(
    entropy_minmax = ifelse(entropy <= entropy_median, "H_etpy", "E_etpy"),
    representation_minmax = ifelse(representation <= representation_median, "E_rep", "H_rep"),
    nCrittersGame_minmax = ifelse(nCrittersGame <= nCrittersGame_median, "H_crits", "E_crits"),
    group = paste(entropy_minmax, representation_minmax, nCrittersGame_minmax, sep = "\n")
  ) %>%
 #group_by(representation_bin, entropy_bin, nCrittersGame_bin, treatment) %>%
  group_by(gameID, treatment)%>%
  mutate(errorAvg = mean(error, na.rm = TRUE)) %>%
  ungroup() # %>%
  #filter(idx == 8)

#print(unique(d.all_minmax %>% select(entropy_median, representation_median, nCrittersGame_median)))

lm_model <- lm(errorAvg ~ group, data = d.all_minmax)

# Calculate center lines and their distances
group_distances <- d.all_minmax %>%
  filter(group !='E_etpy\nH_rep\nE_crits') %>%
  group_by(group, treatment) %>% 
  summarise(median_error = median(errorAvg)) %>%
  pivot_wider(names_from = treatment, values_from = median_error) %>%
  mutate(distance = abs(interactive - slider)) %>%
  arrange(distance)

# Calculate game counts per group and treatment
counts <- d.all_minmax %>%
  filter(group !='E_etpy\nH_rep\nE_crits') %>%
  group_by(group, treatment) %>%
  summarise(nGames = n()) %>%
  pivot_wider(names_from = treatment, values_from = nGames, names_prefix = "nGames_")

# Calculate center lines for group ordering
center_lines <- d.all_minmax %>%
  group_by(group, treatment) %>%
  filter(group !='E_etpy\nH_rep\nE_crits')%>%
  summarise(center_line = median(errorAvg)) %>%
  pivot_wider(names_from = treatment, values_from = center_line) %>%
  mutate(center_line_distance = abs(interactive - slider))

# Reorder groups based on center line distance
d.all_minmax2 <- d.all_minmax %>%
  mutate(group = factor(group, levels = center_lines %>%
                          arrange(center_line_distance) %>%
                          pull(group))) %>% filter(group !='E_etpy\nH_rep\nE_crits') %>% droplevels()

d <-d.all_minmax2 %>%
  ggplot(aes(x = group, y = errorAvg, color = treatment, fill = treatment)) +  
   scale_color_brewer(palette = 'Accent') +
  scale_fill_brewer(palette = 'Accent') + 
  geom_boxplot(alpha = 0.5) +
  #geom_text(data = counts, 
           # aes(x = group, y = Inf, 
                #label = paste0("I: ", nGames_interactive, 
                              # "\nS: ", nGames_slider)),
           # vjust = 1.5, inherit.aes = FALSE) +
  labs(x = "", y = "Error") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 0, hjust = 1),
        legend.position = "top",
        panel.background = element_rect(fill = NA, color = "black"),
        panel.grid = element_blank())
d

#ggsave(
#  "difficulty.png",
#  plot = d,
 # width = 3.5,  
 # height = 10,
#  units = "in",
#  device = "png",
#  dpi = 300 
#)

levels(d.all_minmax2$group)
unique(d.all_minmax2$group)

```

# group v treatment accounting for game noise

```{r}
#d.all_minmax$group <- relevel(d.all_minmax$group, ref = "E_etpy\nE_rep\nE_crits")

d.all_minmax %>%
  lmerTest::lmer(error ~ group *treatment
                   + (1 | gameID), 
       data = ., 
       contrasts = list(treatment = contr.sum(2))) %>% 
  summary()

```

# each difficulty separately accounting for game noise

```{r}
d.all_minmax %>%
  lmerTest::lmer(
    formula = error ~  poly(idx, 2) *treatment * entropy_minmax * representation_minmax * nCrittersGame_minmax + (1 | gameID),
    data = .,
    contrasts = list(
      treatment             = contr.sum,
      entropy_minmax        = contr.sum,
      representation_minmax = contr.sum,
      nCrittersGame_minmax  = contr.sum
    )
  ) %>%
  summary()
```

# confidence of each group

```{r}
d.all_minmax %>%
  lmerTest::lmer(
    formula = confidence ~  poly(idx, 2) *treatment * entropy_minmax * representation_minmax * nCrittersGame_minmax *error + (1 | gameID),
    data = .,
    contrasts = list(
      treatment             = contr.sum,
      entropy_minmax        = contr.sum,
      representation_minmax = contr.sum,
      nCrittersGame_minmax  = contr.sum
    )
  ) %>%
  summary()
```

# error across different groups of difficulty

```{r}

d.all <- d.all %>%
  mutate(
    nCrittersGame_bin = str_remove_all(nCrittersGame_bin, "[\\[\\]()]"),
    entropy_bin = str_remove_all(entropy_bin, "[\\[\\]()]"),
    representation_bin = str_remove_all(representation_bin, "[\\[\\]()]")
  )

heatmap_combined <- bind_rows(
  d.all %>%
    filter(idx == 8) %>%
    group_by(treatment, bin = nCrittersGame_bin) %>%
    summarize(errorAvg = mean(error, na.rm = TRUE), .groups = "drop") %>%
    mutate(variable = "nCritters"),
  
  d.all %>%
    filter(idx == 8) %>%
    group_by(treatment, bin = entropy_bin) %>%
    summarize(errorAvg = mean(error, na.rm = TRUE), .groups = "drop") %>%
    mutate(variable = "entropy"),
  
  d.all %>%
    filter(idx == 8) %>%
    group_by(treatment, bin = representation_bin) %>%
    summarize(errorAvg = mean(error, na.rm = TRUE), .groups = "drop") %>%
    mutate(variable = "representation")
)

p <- ggplot(heatmap_combined, aes(x = bin, y = errorAvg, color = treatment, group = treatment)) +
  geom_point() +
  geom_smooth(method = 'lm', formula = y ~ poly(x, 2), se = FALSE) +
  geom_hline(yintercept = c(0), linetype = 'dotted') +
  scale_color_brewer(palette = 'Accent') +
  theme_few() +
  labs(x = "Bin", y = "Error (Avg)", color = "") +
  facet_wrap(~variable, ncol = 1, scales = "free_x") +
  theme(
    legend.position = 'top',
    axis.text.x = element_text(angle = 15, hjust = 1)  
  )

```

```{r}
d.all_plt <-d.all %>% filter(!is.na(error))

ggplot(d.all_plt, aes(x = nCritters, y = error, color = treatment, group = treatment)) +
  #geom_point() +
  geom_smooth(method = 'lm', se = FALSE) +
 # geom_hline(yintercept = c(0), linetype = 'dotted') +
  scale_color_brewer(palette = 'Accent') +
  theme_few() +
  labs(x = "ncritters", y = "Error", color = "") +
  theme(
    legend.position = 'top',
    axis.text.x = element_text(angle = 15, hjust = 1)  
  )
ggplot(d.all_plt, aes(x = entropy, y = error, color = treatment, group = treatment)) +
  #geom_point() +
  geom_smooth(method = 'lm', se = FALSE) +
 # geom_hline(yintercept = c(0), linetype = 'dotted') +
  scale_color_brewer(palette = 'Accent') +
  theme_few() +
  labs(x = "entropy", y = "Error", color = "") +
  theme(
    legend.position = 'top',
    axis.text.x = element_text(angle = 15, hjust = 1)  
  )
ggplot(d.all_plt, aes(x = representation, y = error, color = treatment, group = treatment)) +
  #geom_point() +
  geom_smooth(method = 'lm', se = FALSE) +
 # geom_hline(yintercept = c(0), linetype = 'dotted') +
  scale_color_brewer(palette = 'Accent') +
  theme_few() +
  labs(x = "representation", y = "Error", color = "") +
  theme(
    legend.position = 'top',
    axis.text.x = element_text(angle = 15, hjust = 1)  
  )
```

representation = round(abs(mleEstimate - mleGame)

# error of number of critters faceted by representation

```{r}
# Clean the bins


# Create combined dataset with errorAvg for each nCrittersGame_bin, faceted by entropy_bin
heatmap_combined <- d.all %>%
  filter(idx == 8) %>%
  group_by(treatment, nCrittersGame_bin, representation_bin) %>%
  summarize(errorAvg = mean(error, na.rm = TRUE), .groups = "drop") %>%
  mutate(variable = "nCritters")

# Plot
ggplot(heatmap_combined, aes(x = nCrittersGame_bin, y = errorAvg, color = treatment, group = treatment)) +
  geom_point() +
  geom_smooth(method = 'lm', formula = y ~ poly(x, 2), se = FALSE) +
  geom_hline(yintercept = c(0), linetype = 'dotted') +
  scale_color_brewer(palette = 'Accent') +
  theme_few() +
  labs(
    x = "",
    y = "Error (Avg)",
    color = ""
  ) +
  facet_wrap(~representation_bin, scales = "free_x") +
  theme(
    aspect.ratio = 1,
    legend.position = 'top',
    axis.text.x = element_text(angle = 45, hjust = 1)
  )

```

```{r}
conflicts_prefer(lmerTest::lmer)
d.all %>%
  ungroup() %>%
  mutate(treatment = fct_relevel(treatment, 'slider', 'interactive')) %>%
  lmer(scale(error) ~ poly(idx, 2) + treatment + (1 + poly(idx, 2) || gameID/playerID),
       data = .,
       contrasts = list(treatment = contr.sum(2)),
       control = lmerControl(optimizer = 'bobyqa')) %>%
  summary()
```

```{r}
d.all %>%
  lmerTest::lmer(error ~ poly(idx, 2) *treatment 
                   + (1 + poly(idx, 1) || gameID) 
                + (1 + poly(idx, 1) || playerID:gameID), 
       data = ., 
       contrasts = list(treatment = contr.sum(2))) %>% 
  summary()

```

```{r}
d.all <- d.all %>%
  mutate(
    scaled_representation = scale(representation),
    scaled_entropy = scale(entropy),
    scaled_nCrittersGame = scale(nCrittersGame),
  )
d.all_1 <- d.all %>%
  filter(idx %in% c(1, 8)) %>%
  group_by(playerID) %>%
  mutate(guessChange = abs(guess[idx == 1] - guess[idx == 8]))

d.all %>% 
  lmerTest::lmer(
    error ~ 
      poly(idx, 2)* scaled_representation * scaled_entropy * treatment * scaled_nCrittersGame +
    (1 | gameID),
    data = .,
    contrasts = list(treatment = contr.sum(2))
  ) %>%
  summary()


```

```{r}

heatmap_combined <- bind_rows(
  d.all_1 %>%
    #filter(idx == 8) %>%
    group_by(treatment, bin = nCrittersGame_bin) %>%
    summarize(errorAvg = mean(error, na.rm = TRUE), .groups = "drop") %>%
    mutate(variable = "nCritters"),
  
  d.all_1 %>%
    #filter(idx == 8) %>%
    group_by(treatment, bin = entropy_bin) %>%
    summarize(errorAvg = mean(error, na.rm = TRUE), .groups = "drop") %>%
    mutate(variable = "entropy"),
  
  d.all_1 %>%
    #filter(idx == 8) %>%
    group_by(treatment, bin = representation_bin) %>%
    summarize(errorAvg = mean(error, na.rm = TRUE), .groups = "drop") %>%
    mutate(variable = "representation")
)

d.all_1 <- d.all_1 %>%
  left_join(heatmap_combined, by = c("treatment", "nCrittersGame_bin" = "bin"))

d.all_1 %>%
  #filter(idx == 8) %>%
  lmerTest::lmer(
    error ~ 
      scaled_representation * treatment +
      scaled_entropy * treatment +
      scaled_nCrittersGame * treatment +
    (1 | gameID),
    data = .,
    contrasts = list(treatment = contr.sum(2))
  ) %>%
  summary()

```

```         
```

## trying to make an error across conditions graph

```{r}
heatmap_test <- d.all %>%
  filter(idx == 8) %>%
  group_by(representation_bin, nCrittersGame_bin) %>%
  summarize(errorAvg = mean(error, na.rm = TRUE))

# new dataframe
diff_error_1 <- d.all %>%
  filter(idx == 8) %>%
  group_by(representation_bin, nCrittersGame_bin, treatment) %>%
  summarize(errorAvg = mean(error, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(names_from = treatment, values_from = errorAvg, names_prefix = "errorAvg_") %>%
  mutate(
    diff_rep_nCritters = errorAvg_slider - errorAvg_interactive,
    diff_rep_entropy = errorAvg_slider - errorAvg_interactive,
    diff_entropy_nCritters = errorAvg_slider - errorAvg_interactive
  )

# new dataframe
diff_error_2 <- d.all %>%
  filter(idx == 8) %>%
  group_by(representation_bin, entropy_bin, treatment) %>%
  summarize(errorAvg = mean(error, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(names_from = treatment, values_from = errorAvg, names_prefix = "errorAvg_") %>%
  mutate(
    diff_rep_nCritters = errorAvg_slider - errorAvg_interactive,
    diff_rep_entropy = errorAvg_slider - errorAvg_interactive,
    diff_entropy_nCritters = errorAvg_slider - errorAvg_interactive
  )

# new dataframe
diff_error_3 <- d.all %>%
  filter(idx == 8) %>%
  group_by(entropy_bin, nCrittersGame_bin, treatment) %>%
  summarize(errorAvg = mean(error, na.rm = TRUE), .groups = "drop") %>%
  pivot_wider(names_from = treatment, values_from = errorAvg, names_prefix = "errorAvg_") %>%
  mutate(
    diff_rep_nCritters = errorAvg_slider - errorAvg_interactive,
    diff_rep_entropy = errorAvg_slider - errorAvg_interactive,
    diff_entropy_nCritters = errorAvg_slider - errorAvg_interactive
  )

```

# error over time for individuals with inaccurate information

```{r}
ggplot(d.all, aes(x = abs((mleEstimate*100)-mleGame*100), y = error, group = idx, color = idx)) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "mleDifference to Error",
       x = "mleDifference",
       y = "Error") +
  theme_minimal() 

```

```{r}
conflicts_prefer(lmerTest::lmer)
d.all %>%
  lmer(error ~ scale(outlierPercent) * scale(idx) + (1 + scale(outlierPercent) + scale(idx) | gameID), 
       data = .) %>% 
  summary()
```

# change from previous guess

```{r}
d.all %>%
  arrange(playerID, idx) %>% 
  group_by(playerID) %>%
  mutate(prevGuess = lag(guess)) %>%
  mutate(distToSelf = abs(guess - prevGuess)) %>%
  filter(idx > 2) %>%
  group_by(idx, treatment) %>%
  tidyboot_mean(distToSelf, na.rm = TRUE) %>%
  ggplot(aes(x = idx, y = empirical_stat, color = treatment)) +
    geom_point() +
    geom_smooth(method = 'lm', formula = y ~ poly(x, 1), se = FALSE) +
    scale_color_brewer(palette = 'Accent') +
    guides(linetype = 'none') +
    scale_x_continuous(breaks = c(2, 4, 6, 8, 10, 12)) +
    labs(y = 'change from previous guess', x = 'reference point (round #)', color = '') +
    theme_few() +
    theme(aspect.ratio = 1, legend.position = 'top')


```

# pull to 50/0/100 values for participants

```{r}
d.all %>%
  ggplot(aes(x = as.numeric(error))) +
    geom_histogram(binwidth =1) +
  #  facet_wrap(~ direction, scales = "free") +
    #xlim(0,100) +
    labs(title = "Distribution of mleEstimate for each treatmentName") +
  theme_few()+facet_wrap(~treatment)
```
