---
title: "Experiment2"
format: html
editor: visual
---

### Import packages

```{r}
library(conflicted)  
conflict_prefer("filter", "dplyr")
conflict_prefer("lag", "dplyr")

library(tidyverse)
library(tidyboot)
library(lme4)
library(here)
library(jsonlite)
library(ggthemes)
```

### Read in data

```{r}
ParseJSONColumn <- function(x) {
  str_c("[ ", str_c(x, collapse = ",", sep=" "), " ]")  %>% 
    fromJSON(flatten = T) 
}

# map game IDs to their treatments
d.treatments.b1 <- read_csv(here('data/experiment2/batch1/games.csv')) %>%
  select(gameID = id, treatmentName) %>% 
  distinct()
d.treatments.b2 <- read_csv(here('data/experiment2/batch2/games.csv')) %>%
  select(gameID = id, treatmentName) %>% 
  distinct()
d.treatments.b3 <- read_csv(here('data/experiment2/batch3/games.csv')) %>%
  select(gameID = id, treatmentName) %>% 
  distinct()
d.treatments.b4 <- read_csv(here('data/experiment2/batch4/games.csv')) %>%
  select(gameID = id, treatmentName) %>% 
  distinct()
d.treatments.b5 <- read_csv(here('data/experiment1/games.csv')) %>%
  select(gameID = id, treatmentName) %>% 
  distinct()
```

```{r}

# map game IDs to their treatments
d.players.b1 <- read_csv(here('data/experiment2/batch1/players.csv')) %>%
  mutate(nSquirrels = str_count(emojiArray, 'ðŸ¿ï¸'),
         nRabbits = str_count(emojiArray, 'ðŸ‡')) %>%
  select(playerID = id, gameID, nSquirrels, nRabbits) %>%
  distinct()

d.players.b2 <- read_csv(here('data/experiment2/batch2/players.csv')) %>%
  mutate(nSquirrels = str_count(emojiArray, 'ðŸ¿ï¸'),
         nRabbits = str_count(emojiArray, 'ðŸ‡')) %>%
  select(playerID = id, gameID, nSquirrels, nRabbits) %>%
  distinct()

d.players.b3 <- read_csv(here('data/experiment2/batch3/players.csv')) %>%
  mutate(nSquirrels = str_count(emojiArray, 'ðŸ¿ï¸'),
         nRabbits = str_count(emojiArray, 'ðŸ‡')) %>%
  select(playerID = id, gameID, nSquirrels, nRabbits) %>%
  distinct()

d.players.b4 <- read_csv(here('data/experiment2/batch4/players.csv')) %>%
  mutate(nSquirrels = str_count(emojiArray, 'ðŸ¿ï¸'),
         nRabbits = str_count(emojiArray, 'ðŸ‡')) %>%
  select(playerID = id, gameID, nSquirrels, nRabbits) %>%
  distinct()

d.players.b5 <- read_csv(here('data/experiment1/players.csv')) %>%
  mutate(nSquirrels = str_count(emojiArray, 'ðŸ¿ï¸'),
         nRabbits = str_count(emojiArray, 'ðŸ‡')) %>%
  select(playerID = id, gameID, nSquirrels, nRabbits) %>%
  distinct()
```

```{r}


# map round IDs to their indices
d.rounds.b1 <- read_csv(here('data/experiment2/batch1/rounds.csv')) %>%
  select(gameID, roundID = id, idx) %>%
  distinct()
d.rounds.b2 <- read_csv(here('data/experiment2/batch2/rounds.csv')) %>%
  select(gameID, roundID = id, idx) %>%
  distinct()
d.rounds.b3 <- read_csv(here('data/experiment2/batch3/rounds.csv')) %>%
  select(gameID, roundID = id, idx) %>%
  distinct()
d.rounds.b4 <- read_csv(here('data/experiment2/batch4/rounds.csv')) %>%
  select(gameID, roundID = id, idx) %>%
  distinct()
d.rounds.b5 <- read_csv(here('data/experiment1/rounds.csv')) %>%
  select(gameID, roundID = id, idx) %>%
  distinct()
```

```{r}

# create long-form dataframe of all messages sent in each game
d.msgs.b1 <- read_csv(here('data/experiment2/batch1/games.csv')) %>% 
  mutate(messages = ifelse(is.na(messages), '[{}]', messages)) %>%
  select(gameID = id, treatmentName, messages) %>%
  mutate(messages = map(messages, .f = ParseJSONColumn)) %>%
  unnest(messages) %>% unnest(messages)
d.msgs.b2 <- read_csv(here('data/experiment2/batch2/games.csv')) %>% 
  mutate(messages = ifelse(is.na(messages), '[{}]', messages)) %>%
  select(gameID = id, treatmentName, messages) %>%
  mutate(messages = map(messages, .f = ParseJSONColumn)) %>%
  unnest(messages) %>% unnest(messages)
d.msgs.b3 <- read_csv(here('data/experiment2/batch3/games.csv')) %>% 
  mutate(messages = ifelse(is.na(messages), '[{}]', messages)) %>%
  select(gameID = id, treatmentName, messages) %>%
  mutate(messages = map(messages, .f = ParseJSONColumn)) %>%
  unnest(messages) %>% unnest(messages)
d.msgs.b4 <- read_csv(here('data/experiment2/batch4/games.csv')) %>% 
  mutate(messages = ifelse(is.na(messages), '[{}]', messages)) %>%
  select(gameID = id, treatmentName, messages) %>%
  mutate(messages = map(messages, .f = ParseJSONColumn)) %>%
  unnest(messages) %>% unnest(messages)
d.msgs.b5 <- read_csv(here('data/experiment1/games.csv')) %>% 
  mutate(messages = ifelse(is.na(messages), '[{}]', messages)) %>%
  select(gameID = id, treatmentName, messages) %>%
  mutate(messages = map(messages, .f = ParseJSONColumn)) %>%
  unnest(messages) %>% unnest(messages)

```

```{r}
# create long-form dataframe of all guesses made in each game
d.guesses.b1 <- read_csv(here('data/experiment2/batch1/playerStages.csv')) %>% 
  select(gameID, roundID, playerID, guess) %>%
  left_join(d.rounds.b1) %>%
  left_join(d.treatments.b1) %>%
  left_join(d.players.b1) %>% 
  distinct()
d.guesses.b2 <- read_csv(here('data/experiment2/batch2/playerStages.csv')) %>% 
  select(gameID, roundID, playerID, guess) %>%
  left_join(d.rounds.b2) %>%
  left_join(d.treatments.b2) %>%
  left_join(d.players.b2) %>% 
  distinct()
d.guesses.b3 <- read_csv(here('data/experiment2/batch3/playerStages.csv')) %>% 
  select(gameID, roundID, playerID, guess) %>%
  left_join(d.rounds.b3) %>%
  left_join(d.treatments.b3) %>%
  left_join(d.players.b3) %>% 
  distinct()
d.guesses.b4 <- read_csv(here('data/experiment2/batch4/playerStages.csv')) %>% 
  select(gameID, roundID, playerID, guess) %>%
  left_join(d.rounds.b4) %>%
  left_join(d.treatments.b4) %>%
  left_join(d.players.b4) %>% 
  distinct()
d.guesses.b5 <- read_csv(here('data/experiment1/playerStages.csv')) %>% 
  select(gameID, roundID, playerID, guess) %>%
  left_join(d.rounds.b5) %>%
  left_join(d.treatments.b5) %>%
  left_join(d.players.b5) %>% 
  distinct()
```

```{r}
d.guesses.b1$treatmentName <- paste0(d.guesses.b1$treatmentName, "-0.7")
d.guesses.b3$treatmentName <- paste0(d.guesses.b3$treatmentName, "-0.3")
d.guesses.b4$treatmentName <- paste0(d.guesses.b4$treatmentName, "-0.3")
```

```{r}
d.guesses <- rbind(d.guesses.b1, d.guesses.b2, d.guesses.b3, d.guesses.b4, d.guesses.b5)
rm(d.guesses.b1,d.guesses.b2,d.guesses.b3,d.guesses.b4,d.guesses.b5,d.msgs.b1,d.msgs.b2,d.msgs.b3,d.msgs.b4,d.msgs.b5,d.players.b1, d.players.b2,d.players.b3,d.players.b4,d.players.b5,d.rounds.b1,
   d.rounds.b2,d.rounds.b3,d.rounds.b4,d.rounds.b5,d.treatments.b1,d.treatments.b2,d.treatments.b3,d.treatments.b4,d.treatments.b5)

```

```{r}
keeper <- d.guesses %>%
  select(gameID, playerID, idx, guess) %>%
  filter(!is.na(guess))

d.guesses <-d.guesses %>% distinct(gameID, playerID, idx, .keep_all = TRUE)

d.guesses <- d.guesses %>%
  left_join(keeper, by = c("gameID", "playerID", "idx")) %>%
  mutate(guess = coalesce(guess.x, guess.y)) %>%
  select(-guess.x, -guess.y)  # Remove redundant columns

d.guesses <- d.guesses %>%  distinct(.keep_all = TRUE)
```

## Implement exclusions

```{r}
playercount <- d.guesses %>%
   filter(idx == 1) %>%
   distinct(playerID, .keep_all = TRUE)
nrow(playercount)

```

```{r}
confused <- d.guesses %>%
  filter(idx == 1) %>%
  mutate(mleEstimate = floor((nRabbits / (nRabbits + nSquirrels)) * 100)) %>%
  mutate(discrepency = abs(guess - mleEstimate)) %>% 
  filter(discrepency > 70) %>% 
  pull(playerID)

```

```{r}
persistentnoClick <- c()  
for (i in 1:7) {
  idx_pair <- c(i, i+1)
  filtered_players <- d.guesses %>%
    group_by(playerID) %>%
    filter(all(is.na(guess[idx %in% idx_pair]))) %>%
    distinct(playerID, .keep_all = TRUE) %>%
    pull(playerID)
  persistentnoClick <- c(persistentnoClick, filtered_players)
}
print(length(unique(persistentnoClick)))

```

```{r}
squares <- c()  
for (i in 1:7) {
  idx_pair <- c(i, i+1)
  filtered_players <- d.guesses %>%
    group_by(playerID) %>%
    filter(all(is.na(guess[idx %in% idx_pair]))) %>%
    distinct(playerID, .keep_all = TRUE) %>%
    pull(playerID)
  squares <- c(squares, filtered_players)
}
print(length(unique(squares)))
```

```{r}
square_games <- d.guesses %>%
  filter(playerID %in% squares) %>%
  group_by(gameID) %>%
  summarize(distinct_playerIDs = n_distinct(playerID))%>%
  filter(distinct_playerIDs != 1)


```

```{r}
#on the issue of so many NAs
hard_clean <- d.guesses %>%
  filter(is.na(guess)) 

playercount_na <- hard_clean %>%
   distinct(playerID, .keep_all = TRUE)
nrow(playercount_na)
#GamingTheSystem is also an exclusion category caluculated in Error

d.guesses %>%
filter(!(playerID %in% unique(hard_clean$gameID))) %>%
  group_by(treatmentName) %>%
  summarize(count = n_distinct(playerID))
d.guesses %>%
   filter(!(gameID %in% unique(hard_clean$gameID))) %>%
   group_by(treatmentName) %>%
   summarize(count = n_distinct(gameID))
fullGames <-d.guesses %>%
   filter(!(gameID %in% unique(hard_clean$gameID)))
```

## Result #1: Convergence

```{r}
d.guesses %>%
  filter(!(playerID %in% persistentnoClick)) %>%
   filter(!(gameID %in% square_games)) %>%
  group_by(treatmentName, idx, gameID) %>%
  summarize(guess = mean(guess, na.rm = TRUE)) %>%
  group_by(treatmentName, idx) %>%
  tidyboot::tidyboot_mean(guess, na.rm = TRUE) %>%
  ggplot(aes(x = idx, y = empirical_stat, color = treatmentName)) +
    geom_point() +
    geom_smooth(method = 'lm', formula = y ~ poly(x, 2), se = F) +
    geom_hline(yintercept = c(30,70), linetype = 'dotted') +
    geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
    theme_few() +
    labs(y = 'average guess', x = 'round #') +
    scale_color_colorblind()
```

## Result #2: Examine error (collapsing across treatment)

## in-game treatment average from the player's critters

```{r}

d.guesses <- d.guesses %>%
  mutate(indvPercent = ifelse(nRabbits > 0 & nSquirrels == 0, 100, 
                   ifelse(nSquirrels > 0 & nRabbits == 0, 1, 
                          ifelse(nRabbits + nSquirrels == 0, 0, 
                                 floor((nRabbits / (nRabbits + nSquirrels)) * 100))))) %>%
  group_by(idx, gameID) %>%
  mutate(nRabbitsGame = sum(nRabbits),
         nSquirrelsGame = sum(nSquirrels)) %>%
  mutate(mleEstimateIndiv = floor((nRabbits / (nRabbits + nSquirrels)) * 100),
         AvgPercent = floor((nRabbitsGame / (nRabbitsGame + nSquirrelsGame)) * 100),
         mleEstimateIndiv = ifelse(is.na(mleEstimateIndiv), 50, mleEstimateIndiv))

d.guesses %>%
  group_by(gameID, treatmentName) %>%
  summarize(mleEstimate = mean(mleEstimateIndiv)) %>%
  ggplot(aes(x = mleEstimate)) +
    geom_histogram(binwidth = 10) +
    facet_wrap(~ treatmentName, scales = "free") +
    labs(title = "Distribution of mleEstimate for each treatmentName")

```

```{r}
trueP <- d.guesses %>%
  group_by(treatmentName) %>%
  summarize(mean_AvgPercent = mean(mleEstimateIndiv, na.rm = TRUE))

d.guesses <- left_join(d.guesses, trueP, by = "treatmentName")

```

```{r}
list <- as.list(as.numeric(trueP$mean_AvgPercent)) 
d.guesses %>%
  filter(!(playerID %in% confused)) %>% 
  filter(!(playerID %in% persistentnoClick)) %>%
  #filter(!(playerID %in% GamingTheSystem)) %>%
  group_by(treatmentName, idx, gameID) %>%
  summarize(guess = mean(guess, na.rm = TRUE)) %>%
  group_by(treatmentName, idx) %>%
  tidyboot::tidyboot_mean(guess, na.rm = TRUE) %>%
  ggplot(aes(x = idx, y = empirical_stat, color = treatmentName)) +
    geom_point() +
    geom_smooth(method = 'lm', formula = y ~ poly(x, 2), se = F) +
  geom_hline(yintercept = c(65,37,64,32), linetype = 'dotted')+
  geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
    theme_few() +
    labs(y = 'average guess', x = 'round #') +
    scale_color_colorblind()
```

## 

```{r}
library(lmerTest)
d.guesses %>%
   filter(!(playerID %in% confused)) %>% 
  filter(!(gameID %in% persistentnoClick)) %>%
  mutate(target = ifelse(treatmentName=='experiment1-0.3', 30, 70),
         error = abs(guess - target)) %>%
  lmerTest::lmer(error ~ poly(idx, 1) + treatmentName
                + (1 + poly(idx, 1) | gameID) 
                + (1 + poly(idx, 1) | playerID:gameID), 
       data = .) %>% 
  summary()
```

```{r}
d.guesses %>%
   filter(!(playerID %in% confused)) %>% 
  filter(!(gameID %in% persistentnoClick)) %>%
  mutate(mleEstimate = 100 * nRabbits / (nRabbits + nSquirrels),
         distance = abs(guess - mleEstimate)) %>%
  lmerTest::lmer(distance ~ poly(idx, 1) + treatmentName
                + (1 + poly(idx, 1) | gameID) 
                + (1 + poly(idx, 1) | playerID:gameID), 
       data = .) %>% 
  summary()
```

```{r}
d.guesses %>%
  filter(!(playerID %in% confused)) %>% 
  filter(!(gameID %in% persistentnoClick)) %>%
  mutate(mleEstimate = 100 * nRabbits / (nRabbits + nSquirrels),
         distance = abs(guess - mleEstimate),
         target = ifelse(treatmentName=='experiment1-0.3', 30, 70),
         error = abs(guess - target)) %>%
  pivot_longer(names_to = 'measure', values_to = 'value', cols = c('distance', 'error')) %>%
  group_by(gameID, idx, measure) %>%
  summarize(value = mean(value, na.rm = TRUE)) %>%
  group_by(idx, measure) %>%
  tidyboot_mean(value, na.rm = TRUE) %>%
  ggplot(aes(x = idx, y = empirical_stat, color = measure)) +
    geom_point() +
    geom_smooth(method = 'lm', formula = y ~ poly(x, 2)) +
    theme_few()

```

## 

# Result #3: Wisdom of Crowds

## participant error without absolute

```{r}
d.guesses <- d.guesses %>%
  mutate(wisError = guess-AvgPercent) %>%
  mutate(treatError = guess-mean_AvgPercent)

```

## average error per player within-game ratios

```{r}
d.guesses %>%
  filter(!(playerID %in% confused)) %>% 
  filter(!(playerID %in% persistentnoClick)) %>%
  filter(!(gameID %in% square_games)) %>%
  group_by(treatmentName, idx) %>%
  tidyboot::tidyboot_mean(wisError, na.rm = TRUE) %>%
  ggplot(aes(x = idx, y = empirical_stat, color = treatmentName)) +
    geom_point() +
    geom_smooth(method = 'lm', formula = y ~ poly(x, 2), se = F) +
    geom_hline(yintercept = c(0), linetype = 'dotted') +
    geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1) +
    theme_few() +
    labs(y = 'average error per player within game', x = 'round #') +
    scale_color_colorblind()
```

## 

## within-game error per player and average

```{r}
d.gameError <- d.guesses %>%
  group_by(gameID) %>%
  summarize(gameError = mean(wisError))

d.guesses <- left_join(d.guesses, d.gameError, by = "gameID")

```

```{r}
# Filter the data frame outside the loop
filtered_df <- d.guesses%>%  
  filter(!(playerID %in% confused)) %>% 
  filter(!(playerID %in% persistentnoClick))#%>%
  #filter(!(playerID %in% GamingTheSystem)) 
# Create a ggplot for error over idx for both treatment names
plot_combined <- 
  ggplot(filtered_df, aes(x = idx, y = wisError, color = treatmentName)) +
  geom_point() +
  geom_smooth(method = 'lm', formula = y ~ poly(x, 2), se = FALSE) +
  geom_hline(yintercept = mean(filtered_df$wisError), linetype = 'dotted') +
  theme_few() +
  labs(y = 'average error per game', x = 'round #') +
  scale_color_colorblind()

# Print the combined plot
print(plot_combined)

```

# Result #4: Does individual data being an outlier create a consistent rate of error

```{r}
d.MLE <- d.guesses %>%
  mutate(outlierPercent = abs(mleEstimateIndiv-AvgPercent))
```

```{r}
# Assuming you have a linear model fit earlier
model <- lm(abs(wisError) ~ outlierPercent, data = d.MLE)

# Calculate the slope difference
slope_difference <- coef(model)[2] - coef(model)[1]

# Now you can use it in the annotate function
ggplot(d.MLE, aes(x = outlierPercent, y = abs(wisError), color = idx)) +
  geom_point() +
  labs(y = "Error", x = "Outlier Percent") +
  ggtitle("Scatter Plot of Outlier Percent vs Error") +
  geom_smooth(method = "lm", se = FALSE, aes(group = idx)) +
  theme_minimal() +
  coord_cartesian(clip = "off") +  
  theme(legend.position = "bottom") + 
  annotate("text", x = max(d.MLE$outlierPercent), y = max(d.MLE$error), 
           label = paste("Change across rounds:", round(slope_difference, 3)),
           hjust = 1, vjust = 1, color = "black", size = 3)

```

```{r}
first <- d.MLE %>%   
  distinct(playerID, .keep_all = TRUE) %>%
  mutate(rounded_outlier = ceiling(outlierPercent/10)*10) %>%
  select(playerID, rounded_outlier)

second <- first %>% ungroup %>%
  select(playerID, rounded_outlier)
d.MLE <- d.MLE %>%
  left_join(select(second, playerID, rounded_outlier), by = "playerID")
```

```{r}
ggplot(d.MLE, aes(x = idx, y = abs(wisError), color = as.factor(rounded_outlier))) +
  geom_point() +
  labs(y = "Error", x = "Time", color = "Outlier Group") +  # Specify legend title here
  ggtitle("Scatter Plot of Error Over Time by Outlier Group") +
  geom_smooth(method = "lm", se = FALSE, aes(group = rounded_outlier)) +
  theme_minimal() +
  coord_cartesian(clip = "off") +  
  theme(legend.position = "bottom")
```

```{r}
validity <- d.MLE %>%   distinct(playerID, .keep_all = TRUE) %>%
  group_by(rounded_outlier) %>%
  summarize(count = n())
print(validity)
```

## Individual MLE

```{r}
d.guesses$individualConsistency <- d.guesses$guess - d.guesses$indvPercent

# Create a line plot
ggplot(d.guesses, aes(x = idx, y = individualConsistency, group = playerID, )) +
  geom_line() +
  geom_point() +
  labs(title = "Player's Guess Difference from Personal Avg Over Time",
       x = "idx",
       y = "Difference (Guess - Truth)",
       color = "Player") +
  theme_minimal()
```

```{r}
ggplot(d.guesses, aes(x = individualConsistency, fill = factor(idx))) +
  geom_density(alpha = 0.5) +
  labs(title = "Density of Player's Guess Difference from Individual Over Time",
       x = "Difference (Guess - Personal p)",
       y = "Density",
       fill = "Round") +
  theme_minimal()
```

# Merged File

```{r}
d.guesses <- d.guesses %>% 
  filter(!(playerID %in% confused)) %>%
  filter(!(playerID %in% persistentnoClick)) %>%
    mutate(treatmentName = case_when(
    treatmentName == "experiment1-0.7" ~ 'unidirectional-0.7',
    treatmentName == "experiment1-0.3" ~ 'unidirectional-0.3',
    treatmentName =="experiment2-interactive-0.3" ~ 'interactive-0.3',
    treatmentName =="experiment2-interactive-0.7" ~ 'interactive-0.7',
    treatmentName =="experiment2-slider-0.3" ~ 'slider-0.3',
    treatmentName =="experiment2-slider-0.7" ~ 'slider-0.7'
  )) %>%
  separate(treatmentName, into = c('condition', 'treatment'), sep = '-') %>%
  filter(!is.na(guess)) %>%
 # left_join(gameCounts) %>%
  mutate(mleEstimateIndiv = floor((nRabbits / (nRabbits + nSquirrels)) * 100), 
         nCrittersGame = nRabbitsGame+nSquirrelsGame,
         mleEstimateGame = floor((nRabbitsGame / (nRabbitsGame + nSquirrelsGame)) * 100),
         mleEstimateIndiv = ifelse(is.na(mleEstimateIndiv), 50, mleEstimateIndiv))  %>%
  arrange(playerID, idx)

```

```{r}
d.guesses %>%   
  filter(!is.na(treatment)) %>%
  group_by(gameID, treatment) %>%
  summarize(mleEstimate = mean(mleEstimateGame)) %>%
  ggplot(aes(x = mleEstimate, fill = treatment)) +
    geom_density(binwidth = 10, alpha = 0.5) +
    theme_few()
```

```{r}
playercount <- d.guesses %>%
   filter(idx == 1) %>%
   distinct(playerID, .keep_all = TRUE) %>% 
  group_by(treatment, condition) %>% 
  tally()

gamecount <- d.guesses %>%
   filter(idx == 1) %>%
   distinct(gameID, .keep_all = TRUE) %>% 
  group_by(treatment, condition) %>% 
  tally()
```

## Result #1: Overall Convergence

```{r}
truePs <- d.guesses %>% 
  filter(idx == 1) %>%
  group_by(condition, treatment, gameID, nSquirrelsGame, nRabbitsGame) %>%
  tally() %>%
  group_by(condition, treatment) %>%
  summarize(trueP = mean(nRabbitsGame / (nSquirrelsGame + nRabbitsGame), na.rm = T))

d.guesses %>%
  group_by(condition, treatment, idx, gameID) %>%
  summarize(guess = mean(guess, na.rm= T)) %>%
  group_by(condition, treatment, idx) %>% 
  tidyboot::tidyboot_mean(guess, na.rm = T) %>%
  left_join(truePs) %>%
  ggplot(aes(x = idx, y = empirical_stat, color = treatment)) +
    geom_smooth(method = 'lm', formula = y ~ poly(x, 2), se = F) +
    geom_hline(aes(yintercept = trueP*100), linetype = 'dotted') +
    theme_few() +
    facet_grid(~ condition) +
    labs(y = 'average guess', x = 'round #') +
    scale_color_colorblind()

```

## Result #2: Examine error (collapsing across treatment)

```{r}
d.guesses %>%
  group_by(treatment, condition, idx, gameID, mleEstimateGame) %>%
  summarize(gameError = mean(guess - mleEstimateGame, na.rm= T)) %>%
  group_by(treatment, condition, idx) %>%
  tidyboot::tidyboot_mean(gameError, na.rm = T) %>%
  ggplot(aes(x = idx, y = empirical_stat, color = condition, group = interaction(condition, treatment))) +
    geom_point() +
    geom_smooth(method = 'lm', formula = y ~ poly(x, 1), se = F) +
    geom_hline(yintercept = c(0), linetype = 'dotted') +
    theme_few() +
    scale_color_colorblind() +
    labs(y = 'average error', x = 'round #') 
```

```{r}
library(lmerTest)
conflicts_prefer(lmerTest::lmer)
d.guesses %>%
  ungroup() %>%
  mutate(condition = fct_relevel(condition, 'slider', 'unidirectional', 'interactive')) %>%
  mutate(error = abs(guess - mleEstimateGame)) %>%
  lmer(scale(error) ~ poly(idx, 2) + condition + (1 + poly(idx, 2) || gameID/playerID),
       data = .,
       contrasts = list(condition = contr.sum(3)),
       control = lmerControl(optimizer = 'bobyqa')) %>%
  summary()
```

```{r}
d.guesses %>%
  group_by(treatment, condition, idx, gameID, mleEstimateGame) %>%
  summarize(error = mean(abs(guess - mleEstimateGame), na.rm= T)) %>%
  group_by(condition, idx) %>%
  tidyboot::tidyboot_mean(error, na.rm = T) %>%
  ggplot(aes(x = idx, y = empirical_stat, color = condition, linetype = condition == 'unidirectional')) +
    geom_point() +
    geom_smooth(method = 'lm', formula = y ~ poly(x, 2), se = F) +
    geom_hline(yintercept = c(0), linetype = 'dotted') +
    theme_few() +
    scale_color_brewer(palette = 'Accent') +
    guides(linetype = 'none') +
    scale_x_continuous(breaks = c(1,3,5,7,9)) +
    labs(y = 'average error', x = 'round #', color = '')  +
    theme(aspect.ratio = 1, legend.position = 'top')
```

# Result #3: Relationship to total information

```{r}
d.guesses %>%
  ungroup() %>%
  group_by(condition, gameID, idx) %>%
  summarize(gameError = abs(mean(mleEstimateGame) - mean(guess, na.rm= T)),
            nCrittersGame = mean(nCrittersGame)) %>%
  ggplot(aes(x = nCrittersGame, y = log1p(gameError), color = condition)) +
    geom_point(alpha = 0.25) +
    geom_smooth(method = 'lm', formula = y ~ poly(x, 1), se = FALSE) +
    theme_few() +
    scale_color_brewer(palette = 'Accent') +
    facet_grid(~ condition) +
    labs(y = 'average error', x = 'total sample size') +
    theme(aspect.ratio = 2, legend.position = 'none')

```

```{r}
m1 <- d.guesses %>%
  ungroup() %>%
  mutate(condition = fct_relevel(condition, 'slider', 'unidirectional', 'interactive')) %>%
  mutate(nCrittersGame = nRabbitsGame + nSquirrelsGame,
         error = abs(guess - mleEstimateGame)) %>%
  lmer(scale(error) ~ condition + poly(nCrittersGame, 2) + idx +  (1 + idx | playerID),
       data = .) 

m2 <- d.guesses %>%
  ungroup() %>%
  mutate(condition = fct_relevel(condition,'unidirectional', 'slider',  'interactive')) %>%
  mutate(nCrittersGame = nRabbitsGame + nSquirrelsGame,
         error = abs(guess - mleEstimateGame)) %>%
  lmer(scale(error) ~ condition * poly(nCrittersGame, 2) + idx + (1 + idx | playerID),
       data = .) 

anova(m1, m2)
summary(m2)
```

# Results #4: Self-weighing

```{r}
d.guesses %>% 
  group_by(playerID) %>%
  mutate(prevGuess = lag(guess)) %>% 
  arrange(playerID, idx) %>%
  mutate(distToSelf = abs(guess - prevGuess)) %>%
  group_by(idx, condition) %>% 
  filter(idx>1) %>%
  tidyboot_mean(distToSelf, na.rm = TRUE) %>%
  ggplot(aes(x = idx, y = empirical_stat, color = condition)) +
    geom_point() +
    geom_smooth(method = 'lm', formula = y~ poly(x, 1), se = F) +
    scale_color_brewer(palette = 'Accent') +
    guides(linetype = 'none') +
    scale_x_continuous(breaks = c(2,4,6,8)) +
    labs(y = 'change from previous guess', x = 'reference point (round #)', color = '') +
    theme_few() +
    theme(aspect.ratio = 1, legend.position = 'top')
```

```{r}
m1 <- d.guesses %>% 
  group_by(playerID) %>%
  mutate(prevGuess = lag(guess)) %>% 
  arrange(playerID, idx) %>%
  mutate(distToSelf = abs(guess - prevGuess)) %>%
  group_by(idx, condition) %>% 
  filter(idx>1) %>%
  lmer(distToSelf ~ poly(idx,2) + condition + (1+ poly(idx,2) | gameID/playerID), 
       data = .)

m2 <- d.guesses %>% 
  group_by(playerID) %>%
  mutate(prevGuess = lag(guess)) %>% 
  arrange(playerID, idx) %>%
  mutate(distToSelf = abs(guess - prevGuess)) %>%
  group_by(idx, condition) %>% 
  filter(idx>1) %>%
  lmer(distToSelf ~ poly(idx,2) * condition + (1+ poly(idx,2) | gameID/playerID), 
       data = .) 

anova(m1,m2)
summary(m1)
```

```{r}
reducedInfo %>%
  select(-`...1`) %>%
  distinct() %>%
  mutate(nCrittersGroup = case_when(
    nCrittersGame >= 10 & nCrittersGame <= 20 ~ 20,
    nCrittersGame >= 21 & nCrittersGame <= 30 ~ 30,
    nCrittersGame >= 31 & nCrittersGame <= 60 ~ 60,
    TRUE ~ NA_real_
  )) %>%
  filter(!is.na(nCrittersGroup)) %>%
#  group_by(treatment, condition, idx, playerID, mleEstimateGame, nCrittersGroup) %>%
  mutate(error = abs(guess - mleEstimateGame),
         nCrittersGame = scale(nCrittersGame),
         idx = scale(idx, scale = F)) %>%
  glmer(error ~ nCrittersGame * condition * idx + (1 + idx | gameID),
       family = 'poisson',
       data = .) %>%
  summary() 
```

```{r}
d.guesses %>%
  mutate(nCrittersGroup = case_when(
    nCrittersGame >= 10 & nCrittersGame <= 20 ~ 20,
    nCrittersGame >= 21 & nCrittersGame <= 30 ~ 30,
    nCrittersGame >= 31 & nCrittersGame <= 40 ~ 40,
    nCrittersGame >= 41 & nCrittersGame <= 50 ~ 50,
    nCrittersGame >= 51 & nCrittersGame <= 60 ~ 60,
    nCrittersGame >= 61 & nCrittersGame <= 70 ~ 70,
    nCrittersGame >= 71 & nCrittersGame <= 80 ~ 80,
    nCrittersGame >= 81 & nCrittersGame <= 90 ~ 90,
    nCrittersGame >= 91 & nCrittersGame <= 100 ~ 100,
    TRUE ~ NA_real_
  )) %>%
  filter(!is.na(nCrittersGroup)) %>%
  filter(condition == 'interactive') %>%
  group_by(nCrittersGroup) %>%
  summarise(unique_games = n_distinct(gameID)) %>%
  print()

d.guesses %>%
  mutate(nCrittersGroup = case_when(
    nCrittersGame >= 10 & nCrittersGame <= 20 ~ 20,
    nCrittersGame >= 21 & nCrittersGame <= 30 ~ 30,
    nCrittersGame >= 31 & nCrittersGame <= 60 ~ 60,

    TRUE ~ NA_real_
  )) %>%
  filter(!is.na(nCrittersGroup)) %>% 
  group_by(treatment, condition, idx, gameID, mleEstimateGame, nCrittersGroup) %>%
  summarize(error = mean(abs(guess - mleEstimateGame), na.rm = TRUE), .groups = 'drop') %>%
  group_by(condition, idx, nCrittersGroup) %>%
  tidyboot::tidyboot_mean(error, na.rm = TRUE) %>%
  filter(condition == 'interactive') %>%
  ggplot(aes(x = idx, y = empirical_stat, color = nCrittersGroup, group = nCrittersGroup, linetype = 'interactive')) +
  geom_point() +
  geom_smooth(method = 'lm', formula = y ~ poly(x, 2), se = FALSE) +
  geom_hline(yintercept = 0, linetype = 'dotted') +
  theme_few() +
  scale_color_gradient(low = "lightgreen", high = "darkgreen") +
  guides(linetype = 'none') +
  scale_x_continuous(breaks = c(1, 3, 5, 7, 9, 11)) +
  labs(y = 'average error', x = 'round #', color = 'nCrittersGroup') +
  theme(aspect.ratio = 1, legend.position = 'top')

```

```{r}
d.guesses %>%
  mutate(nCrittersGroup = case_when(
    nCrittersGame >= 10 & nCrittersGame <= 20 ~ 20,
    nCrittersGame >= 21 & nCrittersGame <= 30 ~ 30,
    nCrittersGame >= 31 & nCrittersGame <= 40 ~ 40,
    nCrittersGame >= 41 & nCrittersGame <= 50 ~ 50,
    nCrittersGame >= 51 & nCrittersGame <= 60 ~ 60,
    nCrittersGame >= 61 & nCrittersGame <= 70 ~ 70,
    nCrittersGame >= 71 & nCrittersGame <= 80 ~ 80,
    nCrittersGame >= 81 & nCrittersGame <= 90 ~ 90,
    nCrittersGame >= 91 & nCrittersGame <= 100 ~ 100,
    TRUE ~ NA_real_
  )) %>%
  filter(!is.na(nCrittersGroup)) %>%
  filter(condition == 'slider') %>%
  group_by(nCrittersGroup) %>%
  summarise(unique_games = n_distinct(gameID)) %>%
  print()
reducedInfo %>%
  mutate(nCrittersGroup = case_when(
    nCrittersGame >= 10 & nCrittersGame <= 20 ~ 20,
    nCrittersGame >= 21 & nCrittersGame <= 30 ~ 30,
    nCrittersGame >= 31 & nCrittersGame <= 50 ~ 50,

    TRUE ~ NA_real_
  )) %>%
  filter(!is.na(nCrittersGroup)) %>%
  group_by(treatment, condition, idx, gameID, mleEstimateGame, nCrittersGroup) %>%
  summarize(error = mean(abs(guess - mleEstimateGame), na.rm = TRUE), .groups = 'drop') %>%
  group_by(condition, idx, nCrittersGroup) %>%
  tidyboot::tidyboot_mean(error, na.rm = TRUE) %>%
  filter(condition == 'slider') %>%
  ggplot(aes(x = idx, y = empirical_stat, color = nCrittersGroup, group = nCrittersGroup, linetype = 'slider')) +
  geom_point() +
  geom_smooth(method = 'lm', formula = y ~ poly(x, 2), se = FALSE) +
  geom_hline(yintercept = 0, linetype = 'dotted') +
  theme_few() +
  scale_color_gradient(low = "lightpink", high = "darkorchid4") +
  guides(linetype = 'none') +
  scale_x_continuous(breaks = c(1, 3, 5, 7, 9, 11)) +
  labs(y = 'average error', x = 'round #', color = 'nCrittersGroup') +
  theme(aspect.ratio = 1, legend.position = 'top')
```

```{r}
reducedInfo %>%
  mutate(nCrittersGroup = case_when(
    nCrittersGame >= 10 & nCrittersGame <= 20 ~ 20,
    nCrittersGame >= 21 & nCrittersGame <= 30 ~ 30,
    nCrittersGame >= 31 & nCrittersGame <= 40 ~ 40,
    nCrittersGame >= 41 & nCrittersGame <= 50 ~ 50,
    nCrittersGame >= 51 & nCrittersGame <= 60 ~ 60,
    nCrittersGame >= 61 & nCrittersGame <= 70 ~ 70,
    nCrittersGame >= 71 & nCrittersGame <= 80 ~ 80,
    nCrittersGame >= 81 & nCrittersGame <= 90 ~ 90,
    nCrittersGame >= 91 & nCrittersGame <= 100 ~ 100,
    TRUE ~ NA_real_
  )) %>%
  filter(!is.na(nCrittersGroup)) %>%
  filter(condition == 'unidirectional') %>%
  group_by(nCrittersGroup) %>%
  summarise(unique_games = n_distinct(gameID)) %>%
  print()
reducedInfo %>%
  mutate(nCrittersGroup = case_when(
    nCrittersGame >= 10 & nCrittersGame <= 20 ~ 20,
    nCrittersGame >= 21 & nCrittersGame <= 30 ~ 30,
    nCrittersGame >= 31 & nCrittersGame <= 50 ~ 50,
    TRUE ~ NA_real_
  )) %>%
  filter(!is.na(nCrittersGroup)) %>%
  group_by(treatment, condition, idx, gameID, mleEstimateGame, nCrittersGroup) %>%
  summarize(error = mean(abs(guess - mleEstimateGame), na.rm = TRUE), .groups = 'drop') %>%
  group_by(condition, idx, nCrittersGroup) %>%
  tidyboot::tidyboot_mean(error, na.rm = TRUE) %>%
  filter(condition == 'unidirectional') %>%
  ggplot(aes(x = idx, y = empirical_stat, color = nCrittersGroup, group = nCrittersGroup, linetype = 'unidirectional')) +
  geom_point() +
  geom_smooth(method = 'lm', formula = y ~ poly(x, 2), se = FALSE) +
  geom_hline(yintercept = 0, linetype = 'dotted') +
  theme_few() +
scale_color_gradient(low = "#FFDAB9", high = "#FF4500")+
  guides(linetype = 'none') +
  scale_x_continuous(breaks = c(1, 3, 5, 7, 9, 11)) +
  labs(y = 'average error', x = 'round #', color = 'nCrittersGroup') +
  theme(aspect.ratio = 1, legend.position = 'top')
```

```{r}
d.guesses %>%
  mutate(nCrittersGroup = case_when(
    nCrittersGame >= 10 & nCrittersGame <= 20 ~ 20,
    nCrittersGame >= 21 & nCrittersGame <= 30 ~ 30,
    nCrittersGame >= 31 & nCrittersGame <= 40 ~ 40,
    nCrittersGame >= 41 & nCrittersGame <= 50 ~ 50,
    nCrittersGame >= 51 & nCrittersGame <= 60 ~ 60,
    nCrittersGame >= 61 & nCrittersGame <= 70 ~ 70,
    nCrittersGame >= 71 & nCrittersGame <= 80 ~ 80,
    nCrittersGame >= 81 & nCrittersGame <= 90 ~ 90,
    nCrittersGame >= 91 & nCrittersGame <= 100 ~ 100,
    TRUE ~ NA_real_
  )) %>%
  filter(!is.na(nCrittersGroup)) %>%
  filter(condition == 'interactive') %>%
  group_by(nCrittersGroup) %>%
  summarise(unique_games = n_distinct(gameID)) %>%
  print()

d.guesses %>%
  mutate(nCrittersGroup = case_when(
    nCrittersGame >= 0 & nCrittersGame <= 10 ~ "0-10",
    nCrittersGame > 10 & nCrittersGame <= 20 ~ "11-20",
    nCrittersGame > 20 & nCrittersGame <= 30 ~ "21-30",
    nCrittersGame > 30 & nCrittersGame <= 40 ~ "31-40",
    TRUE ~ NA_character_
  )) %>%
  filter(!is.na(nCrittersGroup)) %>% 
  group_by(treatment, condition, idx, gameID, mleEstimateGame, nCrittersGroup) %>%
  summarize(error = mean(abs(guess - mleEstimateGame), na.rm = TRUE), .groups = 'drop') %>%
  group_by(condition, idx, nCrittersGroup) %>%
  tidyboot::tidyboot_mean(error, na.rm = TRUE) %>%
  ggplot(aes(x = idx, y = empirical_stat, color = nCrittersGroup, group = nCrittersGroup, linetype = 'interactive')) +
  geom_point() +
  geom_smooth(method = 'lm', formula = y ~ poly(x, 2), se = FALSE) +
  geom_hline(yintercept = 0, linetype = 'dotted') +
  theme_few() +
  scale_color_manual(values = c("0-10" = "lightblue", "11-20" = "blue", "21-30" = "darkblue", "31-40" = "navy")) +
  guides(linetype = 'none') +
  scale_x_continuous(breaks = c(1, 3, 5, 7, 9, 11)) +
  labs(y = 'average error', x = 'round #', color = 'Number of Critters') +
  theme(aspect.ratio = 1, legend.position = 'top')



```
